Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-14 manuscript.tex
Add Frigyesi comments around Ligeti's concepts

TODO Add Frigyesi comments from her paper in the relevant places.

@@

@@

@@

\begin{MyShadequote}
  My reason for so ‘overwriting’ the score was to achieve the effect I wanted, a sense of danger (p.53).
\end{MyShadequote}

>>>>

@@

Indeed, researchers often describe Ligeti's music as pale and nervous dream-like (or even nightmarish) reflection of life.
``Grand emotions are captured in a manner that they do not sound real or believable'' argues Frigyesi, ``gestures exaggerate to the point that it becomes surreal, frightening, absurd, or even comical'' (TODO Frigeyesi).

@@

In addition, researchers pointed out that Ligeti's machines always brake down in his music, what makes them only more frightening (TODO cite).

@@

\begin{MyShadequote}
  My reason for so `overwriting' the score was to achieve the effect I wanted, a sense of danger (p.53).
\end{MyShadequote}
